### 2024-02-18 author-kit-CVPR2024-v2/sec/0_abstract.tex
Formatted header and added abstract for proposal

\begin{abstract}
    Dance is a universal form of expression and entertainment, yet mastering its intricacies
     can be daunting for beginners. To democratize dance learning and make it more accessible
    to enthusiasts, we propose a novel approach utilizing computer vision techniques. By
    breaking down dance videos into vectorized and text-based representations with counts,
    the complexities of dance routines are simplified, enabling easier comprehension and
    replication by average fans.
\end{abstract}

### 2024-02-19 author-kit-CVPR2024-v2/sec/1_intro.tex
Added part of intro, reformatted main.tex to remove extraneous sections

\section{Introduction}
\label{sec:intro}

In recent years, dance has surged in popularity, whether through TikTok trends in younger 
generations, the growing fanbase for elaborate K-pop dance videos, or the performances in 
reality competition shows (which themselves cover wide genres from ballet and contemporary 
to ballroom dances). As a result of this growing interest, many eager dance novices have 
attempted to self-teach from the abundant dance videos online, available through a variety 
of platforms. However, such individuals often struggle with breaking down movements due to 
the speed or intricacy with which they were executed.

We aim to use Computer Vision to partition dance movements into more easily digestible chunks 
by creating a model that can learn (vectorize) dance choreography from a given dance video, and 
output it in a more human-readable form, such as by describing multiple steps in a motion and 
adding counts or timings for context. By developing a tool that provides detailed descriptions 
of human positions and gestures alongside counts or musical beats, learning dance choreographies 
could become much more accessible and approachable for a broader audience.

%-------------------------------------------------------------------------
\subsection{Existing Attempts}

Several existing attempts have been made to tackle the challenge of learning dance from online 
videos, each with its own approach and limitations. One such approach involves platforms that 
generate reskinned versions of dance performances, offering visual references for users. These 
platforms overlay graphics or animations onto the original video, highlighting key movements or 
positions to provide guidance. While these reskinned versions serve as visual aids, they 
typically do not offer active instruction or detailed breakdowns of the dance steps. As a result, 
users may struggle to fully grasp the nuances and intricacies of the movements, limiting the 
effectiveness of this approach as a learning tool.

Another example is a DancePal Hackathon project, which adopts a more technical approach by 
comparing an ideal video with the end user's video skeletons. This method involves analyzing the 
skeletal poses extracted from both videos and identifying discrepancies between them. While this 
approach has the potential to provide personalized feedback to users based on their own performances, 
it comes with several challenges. Firstly, it requires an ideal video with specific lighting, 
background, and perspective conditions to serve as a reference, which may not always be feasible 
to obtain. Additionally, accurately mapping movements onto predefined definitions can be difficult, 
especially for complex dance sequences with varying styles and interpretations. As a result, the 
effectiveness of this approach may be limited by the availability of suitable reference videos and 
the accuracy of the mapping process.

Unlike reskinned versions of dance performances, our proposed method provides detailed instructional 
breakdowns of dance movements, guiding learners through each step with clarity and precision. This 
active instruction facilitates better understanding and retention of choreography. Additionally, our 
method could be expanded to offer personalized feedback based on the analysis of the learner's own 
video and that of an original dance video, ideally without the requirement for perfect lighting or 
camera angle conditions.

\subsection{Useful Techniques}

Several computer vision techniques offer promising avenues for addressing the challenge of learning 
dance from online videos by providing deeper insights into the dynamics and nuances of dance 
movements. One such technique involves exploring 3D models instead of traditional 2D skeletonization
 methods to create more comprehensive representations of dance movements. Unlike 2D skeletonization, 
 which captures only the spatial coordinates of key body joints in a single plane, 3D modeling 
 techniques can capture the full spatial extent of movements, including depth information. This 
 allows for a more accurate and detailed representation of the dancer's body and movements in 
 three-dimensional space, which is particularly valuable for capturing complex and multi-dimensional 
 dance choreographies.

 In addition to 3D modeling, other computer vision techniques such as action recognition, pose 
estimation, trajectory analysis, and video segmentation and tracking can provide valuable insights 
into the dynamics of dance movements. Action recognition algorithms can automatically identify and 
classify different dance gestures and sequences, allowing for automated analysis of choreographic 
patterns and styles. Pose estimation techniques can accurately estimate the skeletal poses of 
dancers from video frames, providing a structural representation of their movements that can be 
used for further analysis and interpretation.

Trajectory analysis techniques can track the trajectories of specific body parts or movements 
over time, allowing for the analysis of movement patterns, velocities, and accelerations. This 
can provide valuable insights into the rhythmic and dynamic aspects of dance performances, 
helping learners to better understand the timing and pacing of movements. Video segmentation and 
tracking methods can segment dance videos into individual sequences or movements, allowing for more 
focused analysis and comparison of specific choreographic elements.

By leveraging these advanced computer vision techniques, learners can gain a deeper understanding 
of the dynamics and nuances of dance movements, facilitating more effective learning experiences. 
These techniques can help learners to break down complex choreographies into smaller, more 
manageable components, identify areas for improvement, and refine their technique with greater 
precision and accuracy. Overall, the integration of computer vision into dance learning has the 
potential to revolutionize the way dance is taught and learned, making it more accessible, engaging, 
and effective for dancers of all levels.

% \subsection{Paper length}
% Papers, excluding the references section, must be no longer than eight pages in length.
% The references section will not be included in the page count, and there is no limit on the length of the references section.
% For example, a paper of eight pages with two pages of references would have a total length of 10 pages.
% {\bf There will be no extra page charges for \confName\ \confYear.}

% Overlength papers will simply not be reviewed.
% This includes papers where the margins and formatting are deemed to have been significantly altered from those laid down by this style guide.
% Note that this \LaTeX\ guide already sets figure captions and references in a smaller font.
% The reason such papers will not be reviewed is that there is no provision for supervised revisions of manuscripts.
% The reviewing process cannot determine the suitability of the paper for presentation in eight pages if it is reviewed in eleven.

% %-------------------------------------------------------------------------
% \subsection{The ruler}
% The \LaTeX\ style defines a printed ruler which should be present in the version submitted for review.
% The ruler is provided in order that reviewers may comment on particular lines in the paper without circumlocution.
% If you are preparing a document using a non-\LaTeX\ document preparation system, please arrange for an equivalent ruler to appear on the final output pages.
% The presence or absence of the ruler should not change the appearance of any other content on the page.
% The camera-ready copy should not contain a ruler.
% (\LaTeX\ users may use options of \texttt{cvpr.sty} to switch between different versions.)

% Reviewers:
% note that the ruler measurements do not align well with lines in the paper --- this turns out to be very difficult to do well when the paper contains many figures and equations, and, when done, looks ugly.
% Just use fractional references (\eg, this line is $087.5$), although in most cases one would expect that the approximate location will be adequate.

% \subsection{Paper ID}
% Make sure that the Paper ID from the submission system is visible in the version submitted for review (replacing the ``*****'' you see in this document).
% If you are using the \LaTeX\ template, \textbf{make sure to update paper ID in the appropriate place in the tex file}.

% \subsection{Mathematics}

% Please number all of your sections and displayed equations as in these examples:
% \begin{equation}
%   E = m\cdot c^2
%   \label{eq:important}
% \end{equation}
% and
% \begin{equation}
%   v = a\cdot t.
%   \label{eq:also-important}
% \end{equation}
% It is important for readers to be able to refer to any particular equation.
% Just because you did not refer to it in the text does not mean some future reader might not need to refer to it.
% It is cumbersome to have to use circumlocutions like ``the equation second from the top of page 3 column 1''.
% (Note that the ruler will not be present in the final copy, so is not an alternative to equation numbers).
% All authors will benefit from reading Mermin's description of how to write mathematics:
% \url{http://www.pamitc.org/documents/mermin.pdf}.

% \subsection{Blind review}

% Many authors misunderstand the concept of anonymizing for blind review.
% Blind review does not mean that one must remove citations to one's own work---in fact it is often impossible to review a paper unless the previous citations are known and available.

% Blind review means that you do not use the words ``my'' or ``our'' when citing previous work.
% That is all.
% (But see below for tech reports.)

% Saying ``this builds on the work of Lucy Smith [1]'' does not say that you are Lucy Smith;
% it says that you are building on her work.
% If you are Smith and Jones, do not say ``as we show in [7]'', say ``as Smith and Jones show in [7]'' and at the end of the paper, include reference 7 as you would any other cited work.

% An example of a bad paper just asking to be rejected:
% \begin{quote}
% \begin{center}
%     An analysis of the frobnicatable foo filter.
% \end{center}

%    In this paper we present a performance analysis of our previous paper [1], and show it to be inferior to all previously known methods.
%    Why the previous paper was accepted without this analysis is beyond me.

%    [1] Removed for blind review
% \end{quote}

% An example of an acceptable paper:
% \begin{quote}
% \begin{center}
%      An analysis of the frobnicatable foo filter.
% \end{center}

%    In this paper we present a performance analysis of the  paper of Smith \etal [1], and show it to be inferior to all previously known methods.
%    Why the previous paper was accepted without this analysis is beyond me.

%    [1] Smith, L and Jones, C. ``The frobnicatable foo filter, a fundamental contribution to human knowledge''. Nature 381(12), 1-213.
% \end{quote}

% If you are making a submission to another conference at the same time, which covers similar or overlapping material, you may need to refer to that submission in order to explain the differences, just as you would if you had previously published related work.
% In such cases, include the anonymized parallel submission~\cite{Authors14} as supplemental material and cite it as
% \begin{quote}
% [1] Authors. ``The frobnicatable foo filter'', F\&G 2014 Submission ID 324, Supplied as supplemental material {\tt fg324.pdf}.
% \end{quote}

% Finally, you may feel you need to tell the reader that more details can be found elsewhere, and refer them to a technical report.
% For conference submissions, the paper must stand on its own, and not {\em require} the reviewer to go to a tech report for further details.
% Thus, you may say in the body of the paper ``further details may be found in~\cite{Authors14b}''.
% Then submit the tech report as supplemental material.
% Again, you may not assume the reviewers will read this material.

% Sometimes your paper is about a problem which you tested using a tool that is widely known to be restricted to a single institution.
% For example, let's say it's 1969, you have solved a key problem on the Apollo lander, and you believe that the 1970 audience would like to hear about your
% solution.
% The work is a development of your celebrated 1968 paper entitled ``Zero-g frobnication: How being the only people in the world with access to the Apollo lander source code makes us a wow at parties'', by Zeus \etal.

% You can handle this paper like any other.
% Do not write ``We show how to improve our previous work [Anonymous, 1968].
% This time we tested the algorithm on a lunar lander [name of lander removed for blind review]''.
% That would be silly, and would immediately identify the authors.
% Instead write the following:
% \begin{quotation}
% \noindent
%    We describe a system for zero-g frobnication.
%    This system is new because it handles the following cases:
%    A, B.  Previous systems [Zeus et al. 1968] did not  handle case B properly.
%    Ours handles it by including a foo term in the bar integral.

%    ...

%    The proposed system was integrated with the Apollo lunar lander, and went all the way to the moon, don't you know.
%    It displayed the following behaviours, which show how well we solved cases A and B: ...
% \end{quotation}
% As you can see, the above text follows standard scientific convention, reads better than the first version, and does not explicitly name you as the authors.
% A reviewer might think it likely that the new paper was written by Zeus \etal, but cannot make any decision based on that guess.
% He or she would have to be sure that no other authors could have been contracted to solve problem B.
% \medskip

% \noindent
% FAQ\medskip\\
% {\bf Q:} Are acknowledgements OK?\\
% {\bf A:} No.  Leave them for the final copy.\medskip\\
% {\bf Q:} How do I cite my results reported in open challenges?
% {\bf A:} To conform with the double-blind review policy, you can report results of other challenge participants together with your results in your paper.
% For your results, however, you should not identify yourself and should not mention your participation in the challenge.
% Instead present your results referring to the method proposed in your paper and draw conclusions based on the experimental comparison to other results.\medskip\\

% \begin{figure}[t]
%   \centering
%   \fbox{\rule{0pt}{2in} \rule{0.9\linewidth}{0pt}}
%    %\includegraphics[width=0.8\linewidth]{egfigure.eps}

%    \caption{Example of caption.
%    It is set in Roman so that mathematics (always set in Roman: $B \sin A = A \sin B$) may be included without an ugly clash.}
%    \label{fig:onecol}
% \end{figure}

% \subsection{Miscellaneous}

% \noindent
% Compare the following:\\
% \begin{tabular}{ll}
%  \verb'$conf_a$' &  $conf_a$ \\
%  \verb'$\mathit{conf}_a$' & $\mathit{conf}_a$
% \end{tabular}\\
% See The \TeX book, p165.

% The space after \eg, meaning ``for example'', should not be a sentence-ending space.
% So \eg is correct, {\em e.g.} is not.
% The provided \verb'\eg' macro takes care of this.

% When citing a multi-author paper, you may save space by using ``et alia'', shortened to ``\etal'' (not ``{\em et.\ al.}'' as ``{\em et}'' is a complete word).
% If you use the \verb'\etal' macro provided, then you need not worry about double periods when used at the end of a sentence as in Alpher \etal.
% However, use it only when there are three or more authors.
% Thus, the following is correct:
%    ``Frobnication has been trendy lately.
%    It was introduced by Alpher~\cite{Alpher02}, and subsequently developed by
%    Alpher and Fotheringham-Smythe~\cite{Alpher03}, and Alpher \etal~\cite{Alpher04}.''

% This is incorrect: ``... subsequently developed by Alpher \etal~\cite{Alpher03} ...'' because reference~\cite{Alpher03} has just two authors.

% \begin{figure*}
%   \centering
%   \begin{subfigure}{0.68\linewidth}
%     \fbox{\rule{0pt}{2in} \rule{.9\linewidth}{0pt}}
%     \caption{An example of a subfigure.}
%     \label{fig:short-a}
%   \end{subfigure}
%   \hfill
%   \begin{subfigure}{0.28\linewidth}
%     \fbox{\rule{0pt}{2in} \rule{.9\linewidth}{0pt}}
%     \caption{Another example of a subfigure.}
%     \label{fig:short-b}
%   \end{subfigure}
%   \caption{Example of a short caption, which should be centered.}
%   \label{fig:short}
% \end{figure*}

### 2024-02-19 author-kit-CVPR2024-v2/sec/1_intro.tex
Finished Proposal Content

@@
 \subsection{Existing Attempts}
-
 Several existing attempts have been made to tackle the challenge of learning dance from online 
@@
 \subsection{Useful Techniques}
-
 Several computer vision techniques offer promising avenues for addressing the challenge of learning 
@@
 and effective for dancers of all levels.
+
+\subsection{Challenges}
+Several challenges arise from attempting this project. One is the quality of input data, which 
+encompasses various factors such as lighting, angles, occlusions, frame rates, and blurring. These 
+factors can significantly impact the accuracy of movement analysis, as they can obscure or distort 
+key visual information needed for understanding dance movements. Addressing these challenges may 
+require the development of robust computer vision algorithms capable of handling noisy or low-quality 
+video data, as well as techniques for preprocessing and enhancing the visual information to improve 
+analysis accuracy.
+
+Moreover, handling interactions between multiple dancers in an ideal video presents additional 
+complexities in accurately capturing and representing dance movements. In many dance performances, 
+especially group or partner dances, dancers may interact with each other in complex ways, such as 
+lifts, partner work, or coordinated movements. Capturing these interactions and accurately 
+representing them in the analysis poses challenges for computer vision algorithms, as they must be 
+able to differentiate between individual dancers and track their movements independently while also 
+accounting for their interactions with others. Addressing this challenge may require the development 
+of advanced tracking and segmentation techniques capable of accurately identifying and tracking 
+multiple dancers in a crowded or dynamic environment.
+
+Overall, addressing these challenges requires a multidisciplinary approach that combines expertise 
+in computer vision, dance analysis, and human-computer interaction. By developing robust algorithms, 
+incorporating domain-specific knowledge, and leveraging advanced techniques for handling complex 
+visual data, it is possible to create a tool that effectively supports learning dance from online 
+videos using computer vision. However, continued research and development efforts are needed to 
+overcome these challenges and realize the full potential of computer vision technology in the 
+field of dance education.
+
+\subsection{Technical Gap}
+The primary aim of this project is to reduce the technical gap between online dance learning resources and 
+effective dance instruction. By enabling the correspondence between individuals with different body proportions 
+captured from various angles, this tool seeks to enhance the accessibility and inclusivity of dance education. 
+This interdisciplinary endeavor involves collaboration between experts in dance, biomechanics, and computer 
+vision, with computer vision providing quantitative analysis capabilities to enhance the understanding and 
+teaching of dance movements.
+
+In conclusion, developing a tool for learning dance from online videos using computer vision holds 
+great potential for revolutionizing dance education and making it more accessible to a wider 
+audience. By leveraging advanced computer vision techniques and interdisciplinary collaboration, 
+this project aims to bridge the gap between online dance resources and effective dance instruction, 
+ultimately empowering individuals to learn and appreciate dance in new and innovative ways.
 

### 2024-02-19 author-kit-CVPR2024-v2/rebuttal.tex
ready to add in-line citations

\documentclass[10pt,twocolumn,letterpaper]{article}
\usepackage[rebuttal]{cvpr}

% Include other packages here, before hyperref.
\usepackage{graphicx}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{booktabs}

% Import additional packages in the preamble file, before hyperref
\input{preamble}

% If you comment hyperref and then uncomment it, you should delete
% egpaper.aux before re-running latex.  (Or just hit 'q' on the first latex
% run, let it finish, and you should be clear).
\definecolor{cvprblue}{rgb}{0.21,0.49,0.74}
\usepackage[pagebackref,breaklinks,colorlinks,citecolor=cvprblue]{hyperref}

% Support for easy cross-referencing
\usepackage[capitalize]{cleveref}
\crefname{section}{Sec.}{Secs.}
\Crefname{section}{Section}{Sections}
\Crefname{table}{Table}{Tables}
\crefname{table}{Tab.}{Tabs.}

% If you wish to avoid re-using figure, table, and equation numbers from
% the main paper, please uncomment the following and change the numbers
% appropriately.
%\setcounter{figure}{2}
%\setcounter{table}{1}
%\setcounter{equation}{2}

% If you wish to avoid re-using reference numbers from the main paper,
% please uncomment the following and change the counter for `enumiv' to
% the number of references you have in the main paper (here, 6).
%\let\oldthebibliography=\thebibliography
%\let\oldendthebibliography=\endthebibliography
%\renewenvironment{thebibliography}[1]{%
%     \oldthebibliography{#1}%
%     \setcounter{enumiv}{6}%
%}{\oldendthebibliography}

%%%%%%%%% PAPER ID  - PLEASE UPDATE
\def\paperID{*****} % *** Enter the Paper ID here
\def\confName{CVPR}
\def\confYear{2023}

\begin{document}

%%%%%%%%% TITLE - PLEASE UPDATE
\title{\LaTeX\ Guidelines for Author Response}  % **** Enter the paper title here

\maketitle
\thispagestyle{empty}
\appendix

%%%%%%%%% BODY TEXT - ENTER YOUR RESPONSE BELOW
\section{Introduction}

After receiving paper reviews, authors may optionally submit a rebuttal to address the reviewers' comments, which will be limited to a {\bf one page} PDF file.
Please follow the steps and style guidelines outlined below for submitting your author response.

The author rebuttal is optional and, following similar guidelines to previous conferences, is meant to provide you with an opportunity to rebut factual errors or to supply additional information requested by the reviewers.
It is NOT intended to add new contributions (theorems, algorithms, experiments) that were absent in the original submission and NOT specifically requested by the reviewers.
You may optionally add a figure, graph, or proof to your rebuttal to better illustrate your answer to the reviewers' comments.

Per a passed 2018 PAMI-TC motion, reviewers should refrain from requesting significant additional experiments for the rebuttal or penalize for lack of additional experiments.
Authors should refrain from including new experimental results in the rebuttal, especially when not specifically requested to do so by the reviewers.
Authors may include figures with illustrations or comparison tables of results reported in the submission/supplemental material or in other papers.

Just like the original submission, the rebuttal must maintain anonymity and cannot include external links that reveal the author identity or circumvent the length restriction.
The rebuttal must comply with this template (the use of sections is not required, though it is recommended to structure the rebuttal for ease of reading).

%-------------------------------------------------------------------------

\subsection{Response length}
Author responses must be no longer than 1 page in length including any references and figures.
Overlength responses will simply not be reviewed.
This includes responses where the margins and formatting are deemed to have been significantly altered from those laid down by this style guide.
Note that this \LaTeX\ guide already sets figure captions and references in a smaller font.

%------------------------------------------------------------------------
\section{Formatting your Response}

{\bf Make sure to update the paper title and paper ID in the appropriate place in the tex file.}

All text must be in a two-column format.
The total allowable size of the text area is $6\frac78$ inches (17.46 cm) wide by $8\frac78$ inches (22.54 cm) high.
Columns are to be $3\frac14$ inches (8.25 cm) wide, with a $\frac{5}{16}$ inch (0.8 cm) space between them.
The top margin should begin 1 inch (2.54 cm) from the top edge of the page.
The bottom margin should be $1\frac{1}{8}$ inches (2.86 cm) from the bottom edge of the page for $8.5 \times 11$-inch paper;
for A4 paper, approximately $1\frac{5}{8}$ inches (4.13 cm) from the bottom edge of the page.

Please number any displayed equations.
It is important for readers to be able to refer to any particular equation.

Wherever Times is specified, Times Roman may also be used.
Main text should be in 10-point Times, single-spaced.
Section headings should be in 10 or 12 point Times.
All paragraphs should be indented 1 pica (approx.~$\frac{1}{6}$ inch or 0.422 cm).
Figure and table captions should be 9-point Roman type as in \cref{fig:onecol}.

List and number all bibliographical references in 9-point Times, single-spaced,
at the end of your response.
% When referenced in the text, enclose the citation number in square brackets, for example~\cite{Alpher05}.
Where appropriate, include the name(s) of editors of referenced books.

\begin{figure}[t]
  \centering
  \fbox{\rule{0pt}{0.5in} \rule{0.9\linewidth}{0pt}}
  %\includegraphics[width=0.8\linewidth]{egfigure.eps}
   \caption{Example of caption.  It is set in Roman so that mathematics
   (always set in Roman: $B \sin A = A \sin B$) may be included without an
   ugly clash.}
   \label{fig:onecol}
\end{figure}

To avoid ambiguities, it is best if the numbering for equations, figures, tables, and references in the author response does not overlap with that in the main paper (the reviewer may wonder if you talk about \cref{fig:onecol} in the author response or in the paper).
See \LaTeX\ template for a workaround.

%-------------------------------------------------------------------------
\subsection{Illustrations, graphs, and photographs}

All graphics should be centered.
Please ensure that any point you wish to make is resolvable in a printed copy of the response.
Resize fonts in figures to match the font in the body text, and choose line widths which render effectively in print.
Readers (and reviewers), even of an electronic copy, may choose to print your response in order to read it.
You cannot insist that they do otherwise, and therefore must not assume that they can zoom in to see tiny details on a graphic.

When placing figures in \LaTeX, it is almost always best to use \verb+\includegraphics+, and to specify the  figure width as a multiple of the line width as in the example below
{\small\begin{verbatim}
   \usepackage{graphicx} ...
   \includegraphics[width=0.8\linewidth]
                   {myfile.pdf}
\end{verbatim}
}

%%%%%%%%% REFERENCES
{
    \small
    \bibliographystyle{ieeenat_fullname}
    \bibliography{main}
}

\end{document}

### 2024-02-19 author-kit-CVPR2024-v2/sec/1_intro.tex
ready to add in-line citations

@@
 overcome these challenges and realize the full potential of computer vision technology in the 
-field of dance education.
+field of dance education.\cite{Authors14b}
 

### 2024-02-19 author-kit-CVPR2024-v2/sec/1_intro.tex
Update 1_intro.tex

@@
 Another example is a DancePal Hackathon project, which adopts a more technical approach by 
-comparing an ideal video with the end user's video skeletons. This method involves analyzing the 
+comparing an ideal video with the end user's video skeletons. \cite{Authors14c} This method involves analyzing the 
 skeletal poses extracted from both videos and identifying discrepancies between them. While this 
@@
  which captures only the spatial coordinates of key body joints in a single plane, 3D modeling 
- techniques can capture the full spatial extent of movements, including depth information. This 
+ techniques can capture the full spatial extent of movements, including depth information. \cite{Alpher03}This 
  allows for a more accurate and detailed representation of the dancer's body and movements in 
@@
 Trajectory analysis techniques can track the trajectories of specific body parts or movements 
-over time, allowing for the analysis of movement patterns, velocities, and accelerations. This 
+over time, allowing for the analysis of movement patterns, velocities, and accelerations. \cite{Alpher02}This 
 can provide valuable insights into the rhythmic and dynamic aspects of dance performances, 

### 2024-02-19 author-kit-CVPR2024-v2/sec/1_intro.tex
Update 1_intro.tex

@@
  three-dimensional space, which is particularly valuable for capturing complex and multi-dimensional 
- dance choreographies.
+ dance choreographies. \cite{Authors14b}
 
@@
 overcome these challenges and realize the full potential of computer vision technology in the 
-field of dance education.\cite{Authors14b}
+field of dance education.
 

### 2024-04-07 author-kit-CVPR2024-v2/sec/1_intro.tex
updated

--- 2024-02-19 author-kit-CVPR2024-v2/sec/1_intro.tex
@@
 
-In recent years, dance has surged in popularity, whether through TikTok trends in younger 
+\indent In recent years, dance has surged in popularity, whether through TikTok trends in younger 
 generations, the growing fanbase for elaborate K-pop dance videos, or the performances in 
@@
 the speed or intricacy with which they were executed.
-
-We aim to use Computer Vision to partition dance movements into more easily digestible chunks 
+\\
+\indent We aim to use Computer Vision to partition dance movements into more easily digestible chunks 
 by creating a model that can learn (vectorize) dance choreography from a given dance video, and 
@@
 \subsection{Existing Attempts}
-Several existing attempts have been made to tackle the challenge of learning dance from online 
+\indent Several existing attempts have been made to tackle the challenge of learning dance from online 
 videos, each with its own approach and limitations. One such approach involves platforms that 
@@
 effectiveness of this approach as a learning tool.
-
-Another example is a DancePal Hackathon project, which adopts a more technical approach by 
-comparing an ideal video with the end user's video skeletons. This method involves analyzing the 
+\\
+\indent Another example is a DancePal Hackathon project, which adopts a more technical approach by 
+comparing an ideal video with the end user's video skeletons\cite{Authors14c}. This method involves analyzing the 
 skeletal poses extracted from both videos and identifying discrepancies between them. While this 
@@
 the accuracy of the mapping process.
-
-Unlike reskinned versions of dance performances, our proposed method provides detailed instructional 
+\\
+\indent Unlike reskinned versions of dance performances, our proposed method provides detailed instructional 
 breakdowns of dance movements, guiding learners through each step with clarity and precision. This 
@@
 \subsection{Useful Techniques}
-Several computer vision techniques offer promising avenues for addressing the challenge of learning 
+\indent Several computer vision techniques offer promising avenues for addressing the challenge of learning 
 dance from online videos by providing deeper insights into the dynamics and nuances of dance 
@@
  which captures only the spatial coordinates of key body joints in a single plane, 3D modeling 
- techniques can capture the full spatial extent of movements, including depth information. This 
+ techniques can capture the full spatial extent of movements, including depth information\cite{Alpher03}. This 
  allows for a more accurate and detailed representation of the dancer's body and movements in 
  three-dimensional space, which is particularly valuable for capturing complex and multi-dimensional 
- dance choreographies.
-
- In addition to 3D modeling, other computer vision techniques such as action recognition, pose 
+ dance choreographies\cite{Authors14b}.
+\\
+\indent In addition to 3D modeling, other computer vision techniques such as action recognition, pose 
 estimation, trajectory analysis, and video segmentation and tracking can provide valuable insights 
@@
 used for further analysis and interpretation.
-
-Trajectory analysis techniques can track the trajectories of specific body parts or movements 
-over time, allowing for the analysis of movement patterns, velocities, and accelerations. This 
+\\
+\indent Trajectory analysis techniques can track the trajectories of specific body parts or movements 
+over time, allowing for the analysis of movement patterns, velocities, and accelerations\cite{Alpher02}. This 
 can provide valuable insights into the rhythmic and dynamic aspects of dance performances, 
@@
 focused analysis and comparison of specific choreographic elements.
-
-By leveraging these advanced computer vision techniques, learners can gain a deeper understanding 
+\\
+\indent By leveraging these advanced computer vision techniques, learners can gain a deeper understanding 
 of the dynamics and nuances of dance movements, facilitating more effective learning experiences. 
@@
 \subsection{Challenges}
-Several challenges arise from attempting this project. One is the quality of input data, which 
+\indent Several challenges arise from attempting this project. One is the quality of input data, which 
 encompasses various factors such as lighting, angles, occlusions, frame rates, and blurring. These 
@@
 analysis accuracy.
-
-Moreover, handling interactions between multiple dancers in an ideal video presents additional 
+\\
+\indent Moreover, handling interactions between multiple dancers in an ideal video presents additional 
 complexities in accurately capturing and representing dance movements. In many dance performances, 
@@
 multiple dancers in a crowded or dynamic environment.
-
-Overall, addressing these challenges requires a multidisciplinary approach that combines expertise 
+\\
+\indent Overall, addressing these challenges requires a multidisciplinary approach that combines expertise 
 in computer vision, dance analysis, and human-computer interaction. By developing robust algorithms, 
@@
 overcome these challenges and realize the full potential of computer vision technology in the 
-field of dance education.\cite{Authors14b}
+field of dance education.
 
 \subsection{Technical Gap}
-The primary aim of this project is to reduce the technical gap between online dance learning resources and 
+\indent The primary aim of this project is to reduce the technical gap between online dance learning resources and 
 effective dance instruction. By enabling the correspondence between individuals with different body proportions 
@@
 teaching of dance movements.
-
-In conclusion, developing a tool for learning dance from online videos using computer vision holds 
+\\
+\indent In conclusion, developing a tool for learning dance from online videos using computer vision holds 
 great potential for revolutionizing dance education and making it more accessible to a wider 

### 2024-04-25 author-kit-CVPR2024-v2/sec/1_intro.tex
updated to PT

@@
 
-\indent In recent years, dance has surged in popularity, whether through TikTok trends in younger 
-generations, the growing fanbase for elaborate K-pop dance videos, or the performances in 
-reality competition shows (which themselves cover wide genres from ballet and contemporary 
-to ballroom dances). As a result of this growing interest, many eager dance novices have 
-attempted to self-teach from the abundant dance videos online, available through a variety 
-of platforms. However, such individuals often struggle with breaking down movements due to 
-the speed or intricacy with which they were executed.
+\indent Over 50 million Americans seek physical therapy every year, whether that be from 
+musculoskeletal conditions, car accidents, or sports injuries. Evidently, there is a large
+need for physical therapy. However, only 35% of PT patients actually adhere to their assigned 
+plan. This is a significant problem since the majority of patients are not following 
+through with their exercises and thus decrease the effectiveness of their therapy plan.
 \\
-\indent We aim to use Computer Vision to partition dance movements into more easily digestible chunks 
-by creating a model that can learn (vectorize) dance choreography from a given dance video, and 
-output it in a more human-readable form, such as by describing multiple steps in a motion and 
-adding counts or timings for context. By developing a tool that provides detailed descriptions 
-of human positions and gestures alongside counts or musical beats, learning dance choreographies 
-could become much more accessible and approachable for a broader audience.
+\indent We aim to use Computer Vision to partition each exercise movement into more easily digestible chunks 
+by creating a model that can learn (vectorize) each exercise movement from two given videos, an instructional 
+one and a patient one, and compare the two. By developing a tool that provides feedback as a result of analyzing 
+the two videos, which ideally should match perfectly, adhering to an exercise plan 
+becomes much more feasible, enjoyable, and even motivating.
 
@@
 \subsection{Existing Attempts}
-\indent Several existing attempts have been made to tackle the challenge of learning dance from online 
-videos, each with its own approach and limitations. One such approach involves platforms that 
-generate reskinned versions of dance performances, offering visual references for users. These 
-platforms overlay graphics or animations onto the original video, highlighting key movements or 
-positions to provide guidance. While these reskinned versions serve as visual aids, they 
-typically do not offer active instruction or detailed breakdowns of the dance steps. As a result, 
-users may struggle to fully grasp the nuances and intricacies of the movements, limiting the 
-effectiveness of this approach as a learning tool.
+\indent Several existing attempts have been made to tackle the challenge of improving patient adherence, 
+each with its own approach and limitations. One such approach involves utilizing monitoring technology, 
+such as pedometers, which have proved to be user-friendly. Though such monitoring technologies are 
+able to monitor, or track, the patients' physical activity decently well, there was not much of an effect in terms 
+of improving their adherence to their exercise plans. As a result, patients using such technologies still struggle with 
+adhering to their exercise plans.
 \\
-\indent Another example is a DancePal Hackathon project, which adopts a more technical approach by 
-comparing an ideal video with the end user's video skeletons\cite{Authors14c}. This method involves analyzing the 
-skeletal poses extracted from both videos and identifying discrepancies between them. While this 
-approach has the potential to provide personalized feedback to users based on their own performances, 
-it comes with several challenges. Firstly, it requires an ideal video with specific lighting, 
-background, and perspective conditions to serve as a reference, which may not always be feasible 
-to obtain. Additionally, accurately mapping movements onto predefined definitions can be difficult, 
-especially for complex dance sequences with varying styles and interpretations. As a result, the 
-effectiveness of this approach may be limited by the availability of suitable reference videos and 
-the accuracy of the mapping process.
+\indent Another attempt that has been made is virtual and augmented reality treatment. Through this method, patients 
+are able to put on their VR headsets and transport into any environment they would like to complete their exercises in. 
+The possibilities are endless: they could surround themselves in peaceful, serene nature, or they could 
+opt for a more competitive gaming atmosphere. Physical therapists have found that this actually 
+makes their treatment plans more appealing and thus improves their patient adherence rates. However, 
+it is important to note that this is significantly more expensive. The cost associated with this 
+method is typically too high for the majority of patients and thus makes this approach less practical.
 \\
-\indent Unlike reskinned versions of dance performances, our proposed method provides detailed instructional 
-breakdowns of dance movements, guiding learners through each step with clarity and precision. This 
-active instruction facilitates better understanding and retention of choreography. Additionally, our 
-method could be expanded to offer personalized feedback based on the analysis of the learner's own 
-video and that of an original dance video, ideally without the requirement for perfect lighting or 
-camera angle conditions.
+\indent Unlike the aforementioned methods, our proposed method is low-cost, accessible, and effective. 
+Implementing the aspect of gamification allows for physical therapy to be fun yet productive. Patients become 
+competitors, working hard to beat their previous scores. Additionally, our method could be expanded to offer 
+further personalized feedback based on the analysis of the learner's own video and the given instructional video, 
+ideally without the requirement for perfect lighting or camera angle conditions.
 
@@
 \indent Several computer vision techniques offer promising avenues for addressing the challenge of learning 
-dance from online videos by providing deeper insights into the dynamics and nuances of dance 
-movements. One such technique involves exploring 3D models instead of traditional 2D skeletonization
- methods to create more comprehensive representations of dance movements. Unlike 2D skeletonization, 
+exercising movements from instructional videos by providing deeper insights into their dynamics and nuances. 
+One such technique involves exploring 3D models instead of traditional 2D skeletonization
+ methods to create more comprehensive representations of the exercise movements. Unlike 2D skeletonization, 
  which captures only the spatial coordinates of key body joints in a single plane, 3D modeling 
- techniques can capture the full spatial extent of movements, including depth information\cite{Alpher03}. This 
- allows for a more accurate and detailed representation of the dancer's body and movements in 
+ techniques can capture the full spatial extent of exericse movements, including depth information\cite{Alpher03}. This 
+ allows for a more accurate and detailed representation of the individual's body and movements in 
  three-dimensional space, which is particularly valuable for capturing complex and multi-dimensional 
- dance choreographies\cite{Authors14b}.
+ exercise movements\cite{Authors14b}.
 \\
@@
 estimation, trajectory analysis, and video segmentation and tracking can provide valuable insights 
-into the dynamics of dance movements. Action recognition algorithms can automatically identify and 
-classify different dance gestures and sequences, allowing for automated analysis of choreographic 
+into the dynamics of exercise movements. Action recognition algorithms can automatically identify and 
+classify different gestures and even exercise sequences, allowing for automated analysis of exercise 
 patterns and styles. Pose estimation techniques can accurately estimate the skeletal poses of 
-dancers from video frames, providing a structural representation of their movements that can be 
+people from video frames, providing a structural representation of their movements that can be 
 used for further analysis and interpretation.
 \\
-\indent Trajectory analysis techniques can track the trajectories of specific body parts or movements 
-over time, allowing for the analysis of movement patterns, velocities, and accelerations\cite{Alpher02}. This 
-can provide valuable insights into the rhythmic and dynamic aspects of dance performances, 
-helping learners to better understand the timing and pacing of movements. Video segmentation and 
-tracking methods can segment dance videos into individual sequences or movements, allowing for more 
-focused analysis and comparison of specific choreographic elements.
+\indent Trajectory analysis techniques can track the trajectories of specific body parts or exercise movements 
+over time, allowing for the analysis of exercise movement patterns, velocities, and accelerations\cite{Alpher02}. This 
+provides valuable insights into the dynamic aspects of these exercises, 
+helping learners to better understand the timing and pacing of the movements. Video segmentation and 
+tracking methods also serve to segment the videos into individual sequences or movements, allowing for more 
+focused analysis and comparison of specific elements.
 \\
 \indent By leveraging these advanced computer vision techniques, learners can gain a deeper understanding 
-of the dynamics and nuances of dance movements, facilitating more effective learning experiences. 
-These techniques can help learners to break down complex choreographies into smaller, more 
+of the dynamics and nuances of exercise movements, facilitating more effective learning experiences. 
+These techniques can help learners to break down complex movements into smaller, more 
 manageable components, identify areas for improvement, and refine their technique with greater 
-precision and accuracy. Overall, the integration of computer vision into dance learning has the 
-potential to revolutionize the way dance is taught and learned, making it more accessible, engaging, 
-and effective for dancers of all levels.
+precision and accuracy. Overall, the integration of computer vision into physical therapy has the 
+potential to revolutionize the way patients approach their recovery plan, making it more accessible, engaging, 
+and effective for patients of all levels.
 
@@
 factors can significantly impact the accuracy of movement analysis, as they can obscure or distort 
-key visual information needed for understanding dance movements. Addressing these challenges may 
+key visual information needed for understanding exercise movements. Addressing these challenges may 
 require the development of robust computer vision algorithms capable of handling noisy or low-quality 
@@
 \\
-\indent Moreover, handling interactions between multiple dancers in an ideal video presents additional 
-complexities in accurately capturing and representing dance movements. In many dance performances, 
-especially group or partner dances, dancers may interact with each other in complex ways, such as 
-lifts, partner work, or coordinated movements. Capturing these interactions and accurately 
-representing them in the analysis poses challenges for computer vision algorithms, as they must be 
-able to differentiate between individual dancers and track their movements independently while also 
-accounting for their interactions with others. Addressing this challenge may require the development 
-of advanced tracking and segmentation techniques capable of accurately identifying and tracking 
-multiple dancers in a crowded or dynamic environment.
+\indent Moreover, handling interactions between multiple persons in an input video presents additional 
+complexities in accurately capturing and representing exercise movements. In some videos, 
+there may be two individuals present that interact with each other in complex ways. It is not uncommon for  
+one to assist the other in certain movements, for example, by helping lift up or stretch their legs. 
+Capturing these interactions and accurately representing them in the analysis poses challenges for 
+computer vision algorithms, as they must be able to differentiate between individuals 
+and track their movements independently while also accounting for their interactions with others. 
+Addressing this challenge may require the development of advanced tracking and segmentation techniques 
+capable of accurately identifying and tracking multiple persons in a dynamic environment.
 \\
 \indent Overall, addressing these challenges requires a multidisciplinary approach that combines expertise 
-in computer vision, dance analysis, and human-computer interaction. By developing robust algorithms, 
+in computer vision, exercise analysis, and human-computer interaction. By developing robust algorithms, 
 incorporating domain-specific knowledge, and leveraging advanced techniques for handling complex 
-visual data, it is possible to create a tool that effectively supports learning dance from online 
+visual data, it is possible to create a tool that effectively supports learning exercises from  
 videos using computer vision. However, continued research and development efforts are needed to 
 overcome these challenges and realize the full potential of computer vision technology in the 
-field of dance education.
+field of physical therapy.
 
 \subsection{Technical Gap}
-\indent The primary aim of this project is to reduce the technical gap between online dance learning resources and 
-effective dance instruction. By enabling the correspondence between individuals with different body proportions 
-captured from various angles, this tool seeks to enhance the accessibility and inclusivity of dance education. 
-This interdisciplinary endeavor involves collaboration between experts in dance, biomechanics, and computer 
+\indent The primary aim of this project is to reduce the technical gap between physical therapy videos and 
+effective recovery plans. By enabling the correspondence between individuals with different body proportions 
+captured from various angles, this tool seeks to enhance the accessibility and inclusivity of these exercises plans. 
+This interdisciplinary endeavor involves collaboration between experts in physical therapy, biomechanics, and computer 
 vision, with computer vision providing quantitative analysis capabilities to enhance the understanding and 
-teaching of dance movements.
+teaching of exercise movements.
 \\
-\indent In conclusion, developing a tool for learning dance from online videos using computer vision holds 
-great potential for revolutionizing dance education and making it more accessible to a wider 
+\indent In conclusion, developing a tool for learning exercises from physical therapy videos using computer vision holds 
+great potential for revolutionizing physical therapy plans and making them more accessible and doable to a wider 
 audience. By leveraging advanced computer vision techniques and interdisciplinary collaboration, 
-this project aims to bridge the gap between online dance resources and effective dance instruction, 
-ultimately empowering individuals to learn and appreciate dance in new and innovative ways.
+this project aims to bridge the gap between physical therapy videos and effective recovery plans, 
+ultimately empowering individuals to learn and appreciate physical therapy in new and innovative ways.
 

### 2024-04-27 author-kit-CVPR2024-v2/sec/1_intro.tex
PT bibliography and citations

@@
 musculoskeletal conditions, car accidents, or sports injuries. Evidently, there is a large
-need for physical therapy. However, only 35% of PT patients actually adhere to their assigned 
-plan. This is a significant problem since the majority of patients are not following 
+need for physical therapy\cite{Authors14i}. However, only 35% of PT patients actually adhere to their assigned 
+plan\cite{Authors14h}. This is a significant problem since the majority of patients are not following 
 through with their exercises and thus decrease the effectiveness of their therapy plan.
@@
 able to monitor, or track, the patients' physical activity decently well, there was not much of an effect in terms 
-of improving their adherence to their exercise plans. As a result, patients using such technologies still struggle with 
+of improving their adherence to their exercise plans\cite{Alpher10}. As a result, patients using such technologies still struggle with 
 adhering to their exercise plans.
@@
 opt for a more competitive gaming atmosphere. Physical therapists have found that this actually 
-makes their treatment plans more appealing and thus improves their patient adherence rates. However, 
+makes their treatment plans more appealing and thus improves their patient adherence rates\cite{Authors14j}. However, 
 it is important to note that this is significantly more expensive. The cost associated with this 

### 2024-04-27 author-kit-CVPR2024-v2/sec/1_intro.tex
typo lol

@@
  which captures only the spatial coordinates of key body joints in a single plane, 3D modeling 
- techniques can capture the full spatial extent of exericse movements, including depth information\cite{Alpher03}. This 
+ techniques can capture the full spatial extent of exercise movements, including depth information\cite{Alpher03}. This 
  allows for a more accurate and detailed representation of the individual's body and movements in 

### 2024-05-04 paper/sec/0_abstract.tex
add files and restructure directories in anticipation of code review

\begin{abstract}
Physical therapy can be likened to a 'rite of passage' that many people go through
because of how common it is. It provides a solution to the patient's problem, whether
that be back pain or a broken leg, but patients must be able to complete their assigned
recovery plans in order to fully heal. To optimize patient recovery, we propose a novel
approach to navigating their recovery plans utilizing computer vision techniques. By
breaking down instruction videos into vectorized representations, we can break down the
patient's videos similarly and compare the two, providing feedback and showing the
patient's progress over time, thus providing motivation in their journey.
\end{abstract}

### 2024-05-04 openpose/python/test.py

@@ -1,0 +1,60 @@
+import cv2
+import openpose_python as op
+
+# Configure OpenPose
+params = {
+    "model_folder": "../models",
+    "hand": False,
+    "face": False,
+    "disable_blending": False,
+    "display": 0,
+}
+
+# Initialize OpenPose
+openpose = op.WrapperPython()
+openpose.configure(params)
+openpose.start()
+
+# Open video file
+video_path = "input_video.mp4"
+cap = cv2.VideoCapture(video_path)
+
+# Get video properties
+frame_width = int(cap.get(cv2.CAP_PROP_FRAME_WIDTH))
+frame_height = int(cap.get(cv2.CAP_PROP_FRAME_HEIGHT))
+fps = int(cap.get(cv2.CAP_PROP_FPS))
+
+# Define the codec and create VideoWriter object
+fourcc = cv2.VideoWriter_fourcc(*'XVID')
+out = cv2.VideoWriter('output_video.avi', fourcc, fps, (frame_width, frame_height))
+
+# Process each frame
+while cap.isOpened():
+    ret, frame = cap.read()
+    if not ret:
+        break
+    
+    # Process the frame with OpenPose
+    datum = op.Datum()
+    datum.cvInputData = frame
+    openpose.emplaceAndPop([datum])
+
+    # Draw skeleton on the frame
+    if datum.poseKeypoints is not None:
+        keypoints = datum.poseKeypoints[0]  # Assuming only one person in the frame
+        for point in keypoints:
+            x, y = int(point[0]), int(point[1])
+            cv2.circle(frame, (x, y), 5, (0, 255, 0), -1)
+
+    # Write the frame to the output video
+    out.write(frame)
+
+    # Display the frame
+    cv2.imshow('Skeletonized Video', frame)
+    if cv2.waitKey(1) & 0xFF == ord('q'):
+        break
+
+# Release video capture and writer
+cap.release()
+out.release()
+cv2.destroyAllWindows()

### 2024-05-04 src/test_player.py

@@ -1,0 +1,119 @@
+import tkinter as tk
+from tkinter import filedialog
+import cv2
+from PIL import Image, ImageTk
+
+class VideoPlayer(tk.Tk):
+    def __init__(self, video1_path, video2_path, start_frame1=0, start_frame2=0):
+        super().__init__()
+        self.title("Side-by-Side Video Player")
+
+        self.video1_path = video1_path
+        self.video2_path = video2_path
+
+        self.video1 = cv2.VideoCapture(video1_path)
+        self.video2 = cv2.VideoCapture(video2_path)
+
+        self.current_frame1 = start_frame1
+        self.current_frame2 = start_frame2
+
+        self.create_widgets()
+        self.play_videos()
+
+    def create_widgets(self):
+        self.video_frame1 = tk.Label(self)
+        self.video_frame1.pack(side=tk.LEFT)
+
+        self.video_frame2 = tk.Label(self)
+        self.video_frame2.pack(side=tk.RIGHT)
+
+        self.frame_num_label1 = tk.Label(self, text="Frame Number 1:")
+        self.frame_num_label1.pack()
+        self.frame_num_entry1 = tk.Entry(self)
+        self.frame_num_entry1.insert(0, str(self.current_frame1))
+        self.frame_num_entry1.pack()
+
+        self.frame_num_label2 = tk.Label(self, text="Frame Number 2:")
+        self.frame_num_label2.pack()
+        self.frame_num_entry2 = tk.Entry(self)
+        self.frame_num_entry2.insert(0, str(self.current_frame2))
+        self.frame_num_entry2.pack()
+
+        self.switch_button = tk.Button(self, text="Switch Videos", command=self.switch_videos)
+        self.switch_button.pack()
+
+        self.create_trackbars()
+
+    def create_trackbars(self):
+        self.trackbar1 = tk.Scale(self, from_=0, to=self.video1.get(cv2.CAP_PROP_FRAME_COUNT)-1,
+                                  orient=tk.HORIZONTAL, command=self.on_trackbar_change1)
+        self.trackbar1.pack()
+        self.trackbar1.set(self.current_frame1)
+
+        self.trackbar2 = tk.Scale(self, from_=0, to=self.video2.get(cv2.CAP_PROP_FRAME_COUNT)-1,
+                                  orient=tk.HORIZONTAL, command=self.on_trackbar_change2)
+        self.trackbar2.pack()
+        self.trackbar2.set(self.current_frame2)
+
[…]

### 2024-05-04 src/test_player.py
Remove unnecessary files

@@ -1,119 +1,0 @@
-import tkinter as tk
-from tkinter import filedialog
-import cv2
-from PIL import Image, ImageTk
-
-class VideoPlayer(tk.Tk):
-    def __init__(self, video1_path, video2_path, start_frame1=0, start_frame2=0):
-        super().__init__()
-        self.title("Side-by-Side Video Player")
-
-        self.video1_path = video1_path
-        self.video2_path = video2_path
-
-        self.video1 = cv2.VideoCapture(video1_path)
-        self.video2 = cv2.VideoCapture(video2_path)
-
-        self.current_frame1 = start_frame1
-        self.current_frame2 = start_frame2
-
-        self.create_widgets()
-        self.play_videos()
-
-    def create_widgets(self):
-        self.video_frame1 = tk.Label(self)
-        self.video_frame1.pack(side=tk.LEFT)
-
-        self.video_frame2 = tk.Label(self)
-        self.video_frame2.pack(side=tk.RIGHT)
-
-        self.frame_num_label1 = tk.Label(self, text="Frame Number 1:")
-        self.frame_num_label1.pack()
-        self.frame_num_entry1 = tk.Entry(self)
-        self.frame_num_entry1.insert(0, str(self.current_frame1))
-        self.frame_num_entry1.pack()
-
-        self.frame_num_label2 = tk.Label(self, text="Frame Number 2:")
-        self.frame_num_label2.pack()
-        self.frame_num_entry2 = tk.Entry(self)
-        self.frame_num_entry2.insert(0, str(self.current_frame2))
-        self.frame_num_entry2.pack()
-
-        self.switch_button = tk.Button(self, text="Switch Videos", command=self.switch_videos)
-        self.switch_button.pack()
-
-        self.create_trackbars()
-
-    def create_trackbars(self):
-        self.trackbar1 = tk.Scale(self, from_=0, to=self.video1.get(cv2.CAP_PROP_FRAME_COUNT)-1,
-                                  orient=tk.HORIZONTAL, command=self.on_trackbar_change1)
-        self.trackbar1.pack()
-        self.trackbar1.set(self.current_frame1)
-
-        self.trackbar2 = tk.Scale(self, from_=0, to=self.video2.get(cv2.CAP_PROP_FRAME_COUNT)-1,
-                                  orient=tk.HORIZONTAL, command=self.on_trackbar_change2)
-        self.trackbar2.pack()
-        self.trackbar2.set(self.current_frame2)
-
[…]

### 2024-05-04 paper/sec/0_abstract.tex
revised abstract

@@
 \begin{abstract}
-Physical therapy can be likened to a 'rite of passage' that many people go through
-because of how common it is. It provides a solution to the patient's problem, whether
-that be back pain or a broken leg, but patients must be able to complete their assigned
-recovery plans in order to fully heal. To optimize patient recovery, we propose a novel
-approach to navigating their recovery plans utilizing computer vision techniques. By
-breaking down instruction videos into vectorized representations, we can break down the
-patient's videos similarly and compare the two, providing feedback and showing the
-patient's progress over time, thus providing motivation in their journey.
+For many individuals facing health hurdles, from common ailments to severe injuries, physical therapy 
+represents a beneficial routine that provides a tangible path to recovery. Because adherence to prescribed 
+recovery plans is critical, we present a novel application of computer vision techniques to supplement the 
+traditional physical therapy experience. Whereas many recent attempts to integrate technology have involved 
+passive data-logging or costly equipment, we aim to provide a cheap but interactive experience revolving 
+around two key features: 1) offer quantitative feedback by scoring patients’ poses and movements against 
+their exercise videos and 2) empower users to curate personalized therapy routines by filtering a database 
+of physical therapy videos with specific poses. In providing a measure of progress and facilitating 
+selection of progressive exercises, we hope to encourage adherence to therapy plans and foster accelerated 
+healing.
+% Physical therapy can be likened to a 'rite of passage' that many people go through
+% because of how common it is. It provides a solution to the patient's problem, whether
+% that be back pain or a broken leg, but patients must be able to complete their assigned
+% recovery plans in order to fully heal. To optimize patient recovery, we propose a novel
+% approach to navigating their recovery plans utilizing computer vision techniques. By
+% breaking down instruction videos into vectorized representations, we can break down the
+% patient's videos similarly and compare the two, providing feedback and showing the
+% patient's progress over time, thus providing motivation in their journey.
 \end{abstract}

### 2024-05-04 paper/sec/3_methods.tex
wrote first two subsections of methods

\section{Methods}
\subsection{Keypoint Detection with OpenPose}
We had three main criteria when selecting an existing library with which to detect body parts.
\begin{enumerate}
    \item The library had to store model outputs in an easily readable, non-proprietary format, such as JSON, 
    so that we could easily work with it.
    \item The model must perform reasonably well on a CPU. When we began our project, we were unsure of how 
    to secure GPU access, and we needed a model that could provide meaningful outputs even if we failed to 
    set up a system for using GPUs.
    \item Ideally, the model possessed capability to detect multiple people in a given frame. Although we did 
    not prioritize our product’s ability to process videos with multiple people, we wanted the flexibility to 
    add that functionality later without a potential overhead from switching our library of choice.
\end{enumerate}
With the above considerations in mind, we evaluated MediaPipe, MoveNet, and OpenPose.

We first explored MediaPipe, a versatile framework by Google that supported vision, natural language, and audio 
tasks. With its lightweight design for on-device ML and target towards time-series data, we found its performance 
promising. However, it appeared to only support single-person pose detection, so we set it aside early on to 
spare our future selves the pain of transitioning to a different library.

We also investigated Tensorflow’s MoveNet, incidentally also part of Google. Built upon MobileNet, it had a 
satisfyingly low resource consumption. However, with the initial configurations that we had tested, it seemed to 
have poor accuracy, with keypoints often hovering in the general region of the desired body parts, but not truly 
aligning with the body joints. Because physical therapy patients may have injuries that cause lower tolerances 
for certain movements, we decided against using MoveNet.

Finally, we decided to try OpenPose. We quickly learned of its ability to output key points from each frame of a 
video as a JSON file. Additionally, not only does OpenPose enable multi-person pose detection, but it also appeared 
to support 3D keypoint detection when two camera perspectives were provided. While we did not plan for the possibility 
of 3D keypoint detection, we were intrigued by the potential, and believed its progress to be evidence that OpenPose 
was still being maintained. Hence, we chose OpenPose for keypoint detection.

While OpenPose does have a higher performance overhead than the other two models, we consider it a worthy trade for the 
improved accuracy and the increased options for input videos (many of which may have more than one person). In fact, while 
testing OpenPose’s hyperparameters, we learned that lowering the video resolution caused a significant speedup in 
processing time, but we were ultimately against reducing the resolution in our input videos because our project 
performance doesn’t depend on low latency, but it does benefit from higher accuracy.

\subsection{Feature Transform}
For a given video, OpenPose outputs a directory of json files, with one for each frame. Before passing these outputs to a 
second machine learning model, we wanted an algorithm that could map similar poses and movements to the same values, 
regardless of camera angle or relative location of the person to the camera. (Due to the nature of OpenPose outputting x, 
y values for keypoints, we have already circumvented the issue of changes in illumination.)  Our keypoint-to-angle algorithm 
aims to:
\begin{itemize}
    \item Greatly reduce the role of absolute pixel locations in identifying features
    \item Make the model invariant to differences in the user’s body structure
    \item Detect straight-line, elliptical, and hybrid motion
\end{itemize}

We choose to transition away from absolute positions due to inspiration from SIFT’s usage of illumination gradients over 
absolute color values. Absolute positions could cause our model to unintentionally train on an individual's location in the 
camera view., y-positions. Similarly, we hoped to make our model invariant to the user’s height and distance from the camera 
(people in the foreground tend to appear taller than people in the background).

Thus, we decided to add some math equations to transform our features from absolute x, y positions to angles between detected 
key points. Additionally, this will likely aid the model in recognizing elliptical motions, which are prevalent in physical 
therapy exercises, as a continuous motion, as opposed to a given, singular elliptical motion being calculated as multiple 
straight-line movements. Additionally, this encodes information about body parts relative to each

### 2024-05-04 paper/sec/3_methods.tex
3.3 detecting poses and gestures

@@
 therapy exercises, as a continuous motion, as opposed to a given, singular elliptical motion being calculated as multiple 
-straight-line movements. Additionally, this encodes information about body parts relative to each
+straight-line movements. Additionally, this encodes information about body parts relative to each other. For 
+instance, moving one’s right hand downwards on the left side of one’s body could be differentiated from moving 
+one’s right hand downwards on the right side of one’s body through the angle of the right elbow relative to 
+the right shoulder.
+
+\subsection{Pose and Gesture Extraction}
+By the temporal nature of videos and humans’ inability to teleport, many frames have body angles that are 
+close in value to those of the neighboring frames, similar to how in images, many pixels may have color 
+values close to their neighbors. It would be inefficient to always work with all of the frames in a given 
+video. In fact, in images, features are often only extracted for corners. We suggest the idea of extracting 
+poses and gestures from videos.
+
+While the algorithm we’ve designed is inspired by the Harris Corner Detector, poses and gestures differ from 
+corners in that we’re not looking for a gradient across all dimensions. Intuitively, this makes sense: even 
+if a person were to stand-in place (not change the angles in their lower body), we would still consider a 
+hand-wave to be a gesture, and raising different hands would be considered different poses.
+
+To reiterate, unlike a corner, which only has two dimensions x and y, a pose or gesture would have as many 
+dimensions as there are angles. Additionally, while corners are detected based on the ratio of the 
+eigenvalues, we’re more concerned with having one strong edge or many weak edges in identifying a gesture: 
+requiring all angles to change would omit basic gestures like a simple hand wave because the majority of 
+angles in the body wouldn’t change. Hence, we use Euclidean Distance as a “change in body position” score.
+
+Another point of interest is that poses would have a low “change in body position” score. Going back to the 
+corner detection analogy, poses are analogous to a flat area within an  image, yet they arguably define a 
+person’s physical actions more than the brief moments of highest “change in body position”. Thus, to extract 
+poses from angles, we actually apply non-minimum suppression (instead of the Harris Corner Detector’s 
+non-maximum suppression) after calculating the Euclidean Distance between angles in adjacent frames.
+
+Meanwhile, we consider a gesture to be the opposite of a pose, a small range of frames when there is a 
+significant “change in body position”. Arguably, a gesture would take place for all the frames between 
+two poses, not just for moments of the fastest “change in body position”. However, because we applied a 
+threshold that selects only a subset of the most significant poses, the above definition may cause multiple 
+gestures to be recognized as one, so we have currently defined a gesture to be three consecutive frames of 
+significant change in angles. (However, it could be interesting to explore modified algorithms for detecting 
+poses and gestures in future work.)

### 2024-05-04 paper/sec/2_litreview.tex
intro and litreview

--- 2024-04-27 author-kit-CVPR2024-v2/sec/1_intro.tex
@@
-\section{Introduction}
-\label{sec:intro}
+\section{Literature Review}
+\label{sec:litreview}
 
-\indent Over 50 million Americans seek physical therapy every year, whether that be from 
-musculoskeletal conditions, car accidents, or sports injuries. Evidently, there is a large
-need for physical therapy\cite{Authors14i}. However, only 35% of PT patients actually adhere to their assigned 
-plan\cite{Authors14h}. This is a significant problem since the majority of patients are not following 
-through with their exercises and thus decrease the effectiveness of their therapy plan.
-\\
-\indent We aim to use Computer Vision to partition each exercise movement into more easily digestible chunks 
-by creating a model that can learn (vectorize) each exercise movement from two given videos, an instructional 
-one and a patient one, and compare the two. By developing a tool that provides feedback as a result of analyzing 
-the two videos, which ideally should match perfectly, adhering to an exercise plan 
-becomes much more feasible, enjoyable, and even motivating.
+\indent Because patient adherence to physical therapy is such a large problem in the healthcare industry, we aim to 
+improve this by assisting physical therapy patients through computer vision techniques. This will positively impact 
+their wellbeing and treatment success rates. Our review explores strategies to enhance adherence, covering existing 
+attempts, key techniques, challenges, and the technical gap. From VR to advanced computer vision, our examination aims 
+to make physical therapy more accessible and effective.
 
@@
 \subsection{Useful Techniques}
-\indent Several computer vision techniques offer promising avenues for addressing the challenge of learning 
-exercising movements from instructional videos by providing deeper insights into their dynamics and nuances. 
+\indent There are many existing computer vision techniques that can be applied to creating an aid for learning exercises. 
 One such technique involves exploring 3D models instead of traditional 2D skeletonization
@@
 estimation, trajectory analysis, and video segmentation and tracking can provide valuable insights 
-into the dynamics of exercise movements. Action recognition algorithms can automatically identify and 
-classify different gestures and even exercise sequences, allowing for automated analysis of exercise 
-patterns and styles. Pose estimation techniques can accurately estimate the skeletal poses of 
+into the dynamics of exercise movements.
+\begin{enumerate}
+  \item Action recognition algorithms can automatically identify and classify different gestures and 
+  even exercise sequences, allowing for automated analysis of exercise patterns and styles.
+  \item Pose estimation techniques can accurately estimate the skeletal poses of 
   people from video frames, providing a structural representation of their movements that can be 
   used for further analysis and interpretation.
-\\
-\indent Trajectory analysis techniques can track the trajectories of specific body parts or exercise movements 
+  \item Trajectory analysis techniques can track the trajectories of specific body parts or exercise movements 
   over time, allowing for the analysis of exercise movement patterns, velocities, and accelerations\cite{Alpher02}. This 
   provides valuable insights into the dynamic aspects of these exercises, 
-helping learners to better understand the timing and pacing of the movements. Video segmentation and 
-tracking methods also serve to segment the videos into individual sequences or movements, allowing for more 
+  helping learners to better understand the timing and pacing of the movements.
+  \item Video segmentation and tracking methods also serve to segment the videos into individual sequences or movements, allowing for more 
   focused analysis and comparison of specific elements.
+\end{enumerate} 
 \\

### 2024-05-04 paper/sec/4_results.tex
4. results

\section{Results}
\label{sec:results}

\indent We had one of our teammates record physical therapy exercises and used those videos to compare with 
the Cornell videos. From the human eye, it looked as though our teammates' video was extremely accurate, and 
our algorithm supported this theory.

\indent Given a pose, we are able to identify similar poses in different videos from a database that we 
curated. This encourages the patient to be more engaged with the exercises, since the exercises do not have to 
 from the medical Cornell database, but rather also from dance.

\subsection{User Customization Options}
\indent Our project offers the user some simple customization options so that it can be catered to individuals. 
These are the difficulty levels and the body part isolation features.

\indent The difficulty is separated into three levels: easy, medium, and hard. Each level has a specific threshold 
of accuracy that is used to score the patient's video: Easy had a threshold of 60, medium 45, and hard 30. The 
difference between the angles of the two videos has to be less than or equal to this threshold to be considered “perfect” for each level.

\indent The project can also isolate specific body parts to score. The accuracy of the exercises takes the whole body into consideration, 
so some body parts that remain idle will raise the accuracy just by being there. This feature allows the patient to decide 
what they want to be scored, so that if there is a specific body part they want to isolate in their practicing, they are 
able to get scores of that accordingly. This feature scores the same way as normal but utilizes the body part extraction feature 
from OpenPose. This can be especially useful if the patient is receiving treatment for a specific body part. For example, if 
they injured their arm, they may want feedback specifically on their arm to see how they are doing.

### 2024-05-04 paper/sec/5_discussion.tex
5. discussion

\section{Discussion}
\label{sec:discussion}

\indent This project had some unexpected setbacks which we worked towards solving.

\indent To identify poses, we needed to find the distances between the angles of frames, 
but we originally had some trouble with the euclidean distance formula. The base formula 
was too sensitive to noise in the movements of the subject, which meant that the algorithm 
was overfitted to the data. By flooring some of the angle gradients, we were able to account 
for noise. This made the algorithm more resistant to slight differences in position, camera 
angle, orientation of the subject, etc.

\indent Initially, the algorithm returned low accuracy scores for two videos that seemed 
otherwise quite similar. In order to ensure that the algorithm was working correctly as 
intended, an example video was run against itself, with an expected and actual accuracy 
result of 100\%. This demonstrated that the algorithm was working but needed to use some 
sort of threshold or margin of error.

\indent We also conducted manual testing ourselves, making sure that the accuracy score 
from the algorithm made sense with the two input videos. For example, if the videos are 
quite similar, we expect a high accuracy score, but if they are vastly different, 
we expect a low accuracy score.

\indent We tested individuals of different heights to ensure that height did not create 
a large difference in terms of accuracy score. For example, if the individual in the 
instruction video is very tall, but the patient is very short and follows the video perfectly, 
the calculation of the angles should ensure that height is not a factor that would limit 
the accuracy score.

### 2024-05-04 paper/sec/6_conclusion.tex
6. conclusion

\section{Conclusion}
\label{sec:conclusion}

\indent Through this project, we were able to utilize computer vision 
techniques to create a program tailored to improve patient adherence to 
recovery plans in physical therapy. We consider this to be the beginning 
of a greater work with its applicability not just in physical therapy 
but also in the healthcare industry and beyond.

\subsection{Limitations}
\indent Although we believe our project proves large progress, it did 
come with its fair share of limitations. As previously stated the camera 
angle between the videos must be the same, otherwise the scores will not 
accurately reflect their performance. This is due to the fact that our 
Gesture Detection algorithm is overly simple.

\indent Another major limitation we faced in the creation of the project 
is the time bottleneck from OpenPose. Due to our restrictions with GPU 
access, we were forced to downscale the data we processed; either 
through resolution or duration. Downscaling the resolution proved to 
reduce the most time, however, it also produced questionable keypoints. 
Thus, for the purpose of testing, we were forced to process shorter 
videos at full resolution, in order to get the most accurate keypoints 
from OpenPose; this resulted in a vast time limitation as a 16-second 
video took 34 minutes to process.

\subsection{Implications}
\indent For future implementations of this project, we would focus on 
matching movements, generate difficulty levels for exercises, and expand 
the scope of the project to also analyze other physical activities.

\indent Currently, our project can match poses, but we would like 
to further develop this to match movements too. This way, if a patient 
wanted to practice a specific motion, like raising the arm, they would 
be able to easily find exercises that would help them practice this.

\indent We would also like to have our project be able to give a 
difficulty rating for exercises as it analyzes the poses. This would be 
so that those in the early stages of physical therapy can see which 
exercises are useful to them.

\indent The final update would be to expand the project’s scope to 
other physical activities. Specifically, we would like to focus on 
dance. The project would be able to determine a dancer’s accuracy, and 
offer many practice dance movements from various genres that the 
dancer can practice with. Another implication could be martial arts, 
which would work in the same way that physical therapy and dance would, 
but be tailored for any unexpected specifications that martial arts 
requires.

### 2024-05-05 paper/sec/3_methods.tex
oops
3. methods

@@
 \section{Methods}
+\label{sec:methods}
+
+\indent We needed to accurately detect keypoints to extract poses and gestures from, and to do this we needed a model that could help us achieve that.
+
 \subsection{Keypoint Detection with OpenPose}
-We had three main criteria when selecting an existing library with which to detect body parts.
+\indent We had three main criteria when selecting an existing library with which to detect body parts.
 \begin{enumerate}
@@
 \end{enumerate}
-With the above considerations in mind, we evaluated MediaPipe, MoveNet, and OpenPose.
+\indent With the above considerations in mind, we evaluated MediaPipe, MoveNet, and OpenPose.
 
-We first explored MediaPipe, a versatile framework by Google that supported vision, natural language, and audio 
+\indent We first explored MediaPipe, a versatile framework by Google that supported vision, natural language, and audio 
 tasks. With its lightweight design for on-device ML and target towards time-series data, we found its performance 
@@
 
-We also investigated Tensorflow’s MoveNet, incidentally also part of Google. Built upon MobileNet, it had a 
+\indent We also investigated Tensorflow’s MoveNet, incidentally also part of Google. Built upon MobileNet, it had a 
 satisfyingly low resource consumption. However, with the initial configurations that we had tested, it seemed to 
@@
 
-Finally, we decided to try OpenPose. We quickly learned of its ability to output key points from each frame of a 
+\indent Finally, we decided to try OpenPose. We quickly learned of its ability to output key points from each frame of a 
 video as a JSON file. Additionally, not only does OpenPose enable multi-person pose detection, but it also appeared 
@@
 
-While OpenPose does have a higher performance overhead than the other two models, we consider it a worthy trade for the 
+\indent While OpenPose does have a higher performance overhead than the other two models, we consider it a worthy trade for the 
 improved accuracy and the increased options for input videos (many of which may have more than one person). In fact, while 
@@
 \subsection{Feature Transform}
-For a given video, OpenPose outputs a directory of json files, with one for each frame. Before passing these outputs to a 
+\indent For a given video, OpenPose outputs a directory of json files, with one for each frame. Before passing these outputs to a 
 second machine learning model, we wanted an algorithm that could map similar poses and movements to the same values, 
@@
 
-We choose to transition away from absolute positions due to inspiration from SIFT’s usage of illumination gradients over 
+\indent We choose to transition away from absolute positions due to inspiration from SIFT’s usage of illumination gradients over 
 absolute color values. Absolute positions could cause our model to unintentionally train on an individual's location in the 
@@
 
-Thus, we decided to add some math equations to transform our features from absolute x, y positions to angles between detected 
+\indent Thus, we decided to add some math equations to transform our features from absolute x, y positions to angles between detected 
 key points. Additionally, this will likely aid the model in recognizing elliptical motions, which are prevalent in physical 
@@
 \subsection{Pose and Gesture Extraction}
-By the temporal nature of videos and humans’ inability to teleport, many frames have body angles that are 
+\indent By the temporal nature of videos and humans’ inability to teleport, many frames have body angles that are 
 close in value to those of the neighboring frames, similar to how in images, many pixels may have color 
@@
 
-While the algorithm we’ve designed is inspired by the Harris Corner Detector, poses and gestures differ from 
+\indent While the algorithm we’ve designed is inspired by the Harris Corner Detector, poses and gestures differ from 
 corners in that we’re not looking for a gradient across all dimensions. Intuitively, this makes sense: even 
@@
 
-To reiterate, unlike a corner, which only has two dimensions x and y, a pose or gesture would have as many 
+\indent To reiterate, unlike a corner, which only has two dimensions x and y, a pose or gesture would have as many 
 dimensions as there are angles. Additionally, while corners are detected based on the ratio of the 
@@
 
-Another point of interest is that poses would have a low “change in body position” score. Going back to the 
+\indent Another point of interest is that poses would have a low “change in body position” score. Going back to the 
 corner detection analogy, poses are analogous to a flat area within an  image, yet they arguably define a 
@@
 
-Meanwhile, we consider a gesture to be the opposite of a pose, a small range of frames when there is a 
+\indent Meanwhile, we consider a gesture to be the opposite of a pose, a small range of frames when there is a 
 significant “change in body position”. Arguably, a gesture would take place for all the frames between 
@@
 poses and gestures in future work.)
+
+\subsection{Distance Evaluation}
+\indent Our project uses three versions of Euclidean Distances for 
+various functions: 1) the default formula identifies poses and gestures 
+and suppress the non-maximum/minimum cases, 2) the formula on a subset 
+of columns to calculate a quantitative score to show the user their 
+similarity to the physical therapy video, and 3) a modified combination 
+of floored angle gradients and weighted Euclidean Distance.
+
+\subsection{Video Selection}
+\indent To test our model, we first selected videos from Cornell 
+University’s CornellHealth website\cite{Alpher11}. These are legitimate 
+physical therapy videos that get prescribed to current patients by their 
+Cornell Health physical therapist, making them an ideal dataset to base 
+our pose estimation model on.
+
+\indent We then completed these exercises ourselves to obtain a sample 
+set of testing videos. We were able to compare the instructional videos 
+with the videos of ourselves following the exercises. The accuracy of 
+our model was determined by comparing our test video with the Cornell 
+video, and determining on our own if the numerical accuracy generated 
+by the model seemed accurate. For example, a patient video following 
+the instructional video perfectly should yield a 100% accuracy score, 
+whereas a patient video that does not follow the instructional video 
+well should yield a lower score.

### 2024-05-05 paper/sec/6_conclusion.tex
updated

@@
 
-\indent Through this project, we were able to utilize computer vision 
+\indent Through this project, we were able to successfully utilize computer vision 
 techniques to create a program tailored to improve patient adherence to 

### 2024-05-05 paper/sec/3_methods.tex
Add files via upload
Update 3_methods.tex

@@
 
+\includegraphics[width=\columnwidth]{sec/openpose_demo}
+\textit{Figure 1. OpenPose in action: pose detection on a frame from an input video of two people. 
+OpenPose accurately detects the key points on both people despite their slightly unorthodox body positions.}
+
 \subsection{Feature Transform}
-\indent For a given video, OpenPose outputs a directory of json files, with one for each frame. Before passing these outputs to a 
+\indent For a given video, OpenPose outputs a directory of JSON files, with one for each frame. Before passing these outputs to a 
 second machine learning model, we wanted an algorithm that could map similar poses and movements to the same values, 

### 2024-05-05 paper/sec/3_methods.tex
Update 3_methods.tex

@@
 aims to:
-\begin{itemize}
+\begin{enumerate}
     \item Greatly reduce the role of absolute pixel locations in identifying features
@@
     \item Detect straight-line, elliptical, and hybrid motion
-\end{itemize}
+\end{enumerate}
 
@@
 absolute color values. Absolute positions could cause our model to unintentionally train on an individual's location in the 
-camera view., y-positions. Similarly, we hoped to make our model invariant to the user’s height and distance from the camera 
+camera view. Similarly, we hoped to make our model invariant to the user’s height and distance from the camera 
 (people in the foreground tend to appear taller than people in the background).
@@
 by the model seemed accurate. For example, a patient video following 
-the instructional video perfectly should yield a 100% accuracy score, 
+the instructional video perfectly should yield a 100\% accuracy score, 
 whereas a patient video that does not follow the instructional video 

### 2024-05-05 paper/sec/3_methods.tex
Update 3_methods.tex

@@
 corners in that we’re not looking for a gradient across all dimensions. Intuitively, this makes sense: even 
-if a person were to stand-in place (not change the angles in their lower body), we would still consider a 
+if a person were to stand in place (not change the angles in their lower body), we would still consider a 
 hand-wave to be a gesture, and raising different hands would be considered different poses.

### 2024-05-05 paper/sec/3_methods.tex

@@
 corner detection analogy, poses are analogous to a flat area within an  image, yet they arguably define a 
-person’s physical actions more than the brief moments of highest “change in body position”. Thus, to extract 
+person’s physical actions more than the brief moments of highest “change in body position.” Thus, to extract 
 poses from angles, we actually apply non-minimum suppression (instead of the Harris Corner Detector’s 
@@
 \indent Meanwhile, we consider a gesture to be the opposite of a pose, a small range of frames when there is a 
-significant “change in body position”. Arguably, a gesture would take place for all the frames between 
-two poses, not just for moments of the fastest “change in body position”. However, because we applied a 
+significant “change in body position.” Arguably, a gesture would take place for all the frames between 
+two poses, not just for moments of the fastest “change in body position.” However, because we applied a 
 threshold that selects only a subset of the most significant poses, the above definition may cause multiple 

### 2024-05-05 paper/sec/6_conclusion.tex
Update 6_conclusion.tex

@@
 \subsection{Limitations}
-\indent Although we believe our project proves large progress, it did 
+\indent Although we believe our project proves great advancement, it did 
 come with its fair share of limitations. As previously stated the camera 
@@
 is the time bottleneck from OpenPose. Due to our restrictions with GPU 
-access, we were forced to downscale the data we processed; either 
+access, we were forced to downscale the data we processed, either 
 through resolution or duration. Downscaling the resolution proved to 
-reduce the most time, however, it also produced questionable keypoints. 
+reduce the most time; however, it also produced questionable keypoints. 
 Thus, for the purpose of testing, we were forced to process shorter 
@@
 other physical activities. Specifically, we would like to focus on 
-dance. The project would be able to determine a dancer’s accuracy, and 
+dance. The project would be able to determine a dancer’s accuracy and 
 offer many practice dance movements from various genres that the 
